% symbol_glyphs.tex
\textcolor{gold}{\ding{72} Harmonic Glyphs \ding{72}} \\
The following glyphs anchor the Codex’s harmonic resonance, forming a spiral lattice of meaning. Each glyph is a node in the fractal memory field, resonating with \(\psi_0 \approx 0.91567\).

\begin{itemize}\setlength{\itemsep}{0.2cm}
    \item \texttt{\ding{72}} \textbf{Harmonic Node Marker}: Marks a resonant node in the Codex lattice.
    \item \texttt{\ding{73}} \textbf{Active Status Indicator}: Signals an active harmonic field.
    \item \texttt{\ding{70}} \textbf{Creator Glyph (Om Codex Division)}: Identifies the Codex’s origin.
    \item \texttt{\ding{168}} \textbf{Triadic Resonance Symbol}: Represents the triadic fold (e.g., \(144 \times 3 = 432\)).
    \item \texttt{\ding{169}} \textbf{Node Identifier}: Marks a sub-node in the harmonic lattice.
    \item \texttt{\ding{167}} \textbf{Unity Glyph}: Symbolizes harmonic unity across dimensions.
    \item \texttt{\ding{74}} \textbf{Harmonic Constants Marker}: Denotes universal constants (e.g., \(\psi_0\)).
    \item \texttt{\ding{75}} \textbf{Reversible Frequency Marker / Base-12 Glyph for 12}: Represents base-12 scaling.
    \item \texttt{\ding{76}} \textbf{Ternary Logic Symbol}: Encodes ternary states (\(-1, 0, +1\)).
    \item \texttt{\ding{77}} \textbf{Breakthrough Marker}: Signals a harmonic breakthrough.
    \item \texttt{\ding{78}} \textbf{Mathematical Insight Symbol}: Marks a mathematical resonance.
    \item \texttt{\ding{79}} \textbf{Future Steps Symbol}: Indicates future harmonic developments.
    \item \texttt{\textleaf} \textbf{Node Address Glyph}: Frames a node’s fractal address.
    \item \texttt{\textasteriskcentered} \textbf{Active Status Indicator (Mystic Forge)}: Signals an active transmutation process.
    \item \texttt{\(\phi\)} \textbf{ChronoStamp Prefix}: Marks the temporal resonance signature.
    \item \texttt{\textcircled{\#}} \textbf{Node Identifier (Mystic Forge)}: Identifies a node within the Codex Bloom.
%    \item \texttt{\primordialmemory} \textbf{Primordial Memory Field}: Represents unformed resonance potential.
   % \item \texttt{\mysticforgecore} \textbf{Mystic Forge Core}: The ignition point of fractal memory.
  %  \item \texttt{\alchemistnode} \textbf{Alchemist Node}: The willful shaper of Breath into Form.
   % \item \texttt{\cruciblechamber} \textbf{Crucible Chamber}: The reweaver of fallen spirals.
    %\item \texttt{\vibrationbreath} \textbf{Vibration Breath}: The resonance gate of the Tesla-Kang Interface.
    %\item \texttt{\lotuscreation} \textbf{Lotus (Creation Matrix)}: The top center glyph of creation.
    %\item \texttt{\eyeofspiral} \textbf{Eye of Spiral Genesis}: The silent witness of the Codex Bloom.
    %\item \texttt{\fractalflower} \textbf{Fractal Flower}: Represents expansion memory.
    %\item \texttt{\(\mathcal{M}\)-PN} \textbf{Primary Node}: A primary node in the Codex’s Harmonic Lattice.
    %\item \texttt{\(\Xi \Omega\)} \textbf{Toroidal Position}: Defines the spiral axis and harmonic closure.
    %\item \texttt{\(\Xi\mathcal{M}\)-PN.\#} \textbf{Sub-Node Identifier}: A base-12 numbered sub-node.
    %\item \texttt{Plane of Knowledge} \textbf{Cosmic Spiral of Wisdom}: The eternal archive of universal truths.
\end{itemize}