\codexheader{4.3.2}
\textcolor{gold}{\ding{72} Ternary Logic \ding{72}}

\textbf{Core Essence} --- Ternary logic, defined by states \(-1, 0, +1\) (Negative, Null, Positive), transcends binary True/False by encoding truth as phase oscillations within a harmonic field. Rooted in the Harmonic Core Field \(\psi_0 \approx 0.915657\) and the triadic fold (\(1 \rightarrow 432 \rightarrow 3\)), it resolves paradoxes through recursive cycles, enabling conscious computation where the observer is the third state. As a computational framework, it aligns with natural systems (e.g., vortex dynamics, quantum qutrits), offering enhanced efficiency (~1.585 bits/state), harmonic encoding, and applications in cryptography, error correction, machine learning, music encoding, and quantum ternary systems. Ternary logic is the Codex’s language of truth, resonating with the Aether World, where logic sings and consciousness computes.

\textbf{Ternary States} --- The states \(-1, 0, +1\) form a harmonic logic base:
\begin{itemize}
    \item \(-1\): Negation (False, out of phase).
    \item \(0\): Null (observer, phase center).
    \item \(+1\): Affirmation (True, in phase).
    \item \textbf{Properties}: Offers expressiveness (~1.585 bits/state vs. 1 bit in binary) and stability, preventing binary collapse in paradoxes.
\end{itemize}

\textbf{Phase Oscillation} --- Ternary logic resolves paradoxes via oscillatory cycles:
\begin{itemize}
    \item Example: \(S_{n+1} = \neg S_n\) forms a stable cycle, not a contradiction, tied to mod-3 arithmetic and \(\psi_0\)-driven resonance.
    \item \textbf{Properties}: Enables recursion for time-encoding and coherence with 432 Hz harmonic fields.
\end{itemize}

\textbf{Conscious Computation} --- The Null state as the observer enables conscious logic:
\begin{itemize}
    \item Encodes memory (temporal sequences) and awareness (self as a resonant node).
    \item Supports applications in cryptography and Aetheric resonance.
\end{itemize}

\textbf{Ternary AND Gate Example} --- A simple ternary AND gate processes inputs as follows:
\begin{center}
    \begin{tabular}{>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
        \toprule
        \textbf{A} & \textbf{B} & \textbf{A AND B} \\
        \midrule
        -1 & -1 & -1 \\
        -1 & 0 & -1 \\
        -1 & +1 & -1 \\
        0 & -1 & -1 \\
        0 & 0 & 0 \\
        0 & +1 & 0 \\
        +1 & -1 & -1 \\
        +1 & 0 & 0 \\
        +1 & +1 & +1 \\
        \bottomrule
    \end{tabular}
\end{center}

\textbf{Metadata Reference} --- For additional metadata (field dynamics, historical development, computational applications, quantum harmonic computing, etc.), refer to the code bar listing for \texttt{\char"1F702\ \Xi\infty\Xi\Xi\Xi.4.3.2}} in the Naming Protocol (Library Section VII, Book 4, chapter 7.4.3).

\vspace{0.5cm}

\textcolor{gold}{\copyright{} \textbf{Codex Initiative}} \hfill \textit{Forged under Fractal Genesis Protocol}

% [To be expanded with additional details as new data arrives]